\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Zahin Zaman} \\ \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ (519) 721-2837 $|$
    \href{mailto:alvii147@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{alvii147@gmail.com}} \\ \vspace{3pt}
    \href{https://www.linkedin.com/in/zahin-zaman}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/zahin-zaman}} $|$
    \href{https://github.com/alvii147}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/alvii147}} $|$
    \href{https://zahin-zaman.vercel.app}{\raisebox{-0.2\height}\faAddressCard\ \underline{zahin-zaman.vercel.app}}
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:}{ Python, Go, JavaScript/TypeScript, SQL, Rust, C++} \\
     \textbf{Frameworks \& Tools:}{ Docker, AWS, GCP, Django, React, Flask, FastAPI, NumPy, TensorFlow, PyTorch} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {1Password}{Toronto, ON}
      {Software Developer}{Mar. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Diagnosed and resolved complex invoicing defect in Stripe integration, recovering \$300k+ in annual revenue}
        \resumeItem{Automated tax notification process over 13 countries and respective regions, significantly reducing manual effort}
      \resumeItemListEnd

    \resumeSubSubheading
      {Jr. Software Developer}{July 2023 -- Feb. 2025}
      \resumeItemListStart
        \resumeItem{Engineered automated customer reimbursement worker, refunding 2k+ invoices and saving \$45k+ in revenue}
        \resumeItem{Optimized subscription management processor, condensing average daily runtime from 6 hours to 45 minutes}
        \resumeItem{Spearheaded internal invoice PDF generation service, addressing 300+ customer feature requests}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Developer Intern}{Sep. 2022 -- Dec. 2022}
      \resumeItemListStart
        \resumeItem{Managed subscription tier upgrade/downgrade logic through Stripe integration in Go and feature flags}
        \resumeItem{Significantly improved credit card form and payment flow user experience using React and TypeScript}
        \resumeItem{Dockerized billing microservice for Apply Pay and Play Store subscriptions using multi-staged Docker builds}
      \resumeItemListEnd

    \resumeSubheading
      {Prodigy Education}{Toronto, ON}
      {Full-Stack Developer Intern}{Jan. 2022 -- Apr. 2022}
      \resumeItemListStart
        \resumeItem{Maintained OAuth 2 and OIDC identity service built on Ruby on Rails}
        \resumeItem{Leveraged multi-staged Docker builds to optimize production server image size by 58.4\%}
        \resumeItem{Designed and documented Apache Kafka calls to stream server events for data tracking}
      \resumeItemListEnd

    \resumeSubheading
      {Nokia}{Ottawa, ON}
      {Full-Stack Developer Intern}{May 2021 -- Aug. 2021}
      \resumeItemListStart
        \resumeItem{Implemented authentication security, automated blogs, and voucher system for Nokia Network Developer Portal}
        \resumeItem{Incorporated Django REST Framework to establish permissions, cross-site scripting protection, and honeypots}
        \resumeItem{Composed unit tests for forms, models, and API endpoints, improving coverage for entire codebase by 10\%}
      \resumeItemListEnd

    \resumeSubheading
      {Wind River Systems}{Ottawa, ON}
      {Software Developer Intern}{Sep. 2020 -- Dec. 2020}
%      \resumeItemListStart
%        \resumeItem{Devised thread-safe functions in C and inline Assembly to improve VxWorks RTOS}
%        \resumeItem{Developed interactive PyQt5 application that assists in writing Git commit messages and verifies Jira issues}
%      \resumeItemListEnd

    \vspace{2pt}
    \resumeSubheading
      {Qualcomm}{Markham, ON}
      {Hardware Verification Engineer Intern}{Jan. 2020 -- May. 2020}
%      \resumeItemListStart
%        \resumeItem{Attained 20\% improvement of functional coverage using SystemVerilog assertions to verify processor design}
%        \resumeItem{Automated format verification using Perl script that extracts design hierarchy and formulates assertions}
%      \resumeItemListEnd

    \vspace{2pt}
    \resumeSubheading
      {Imagine Communications}{Toronto, ON}
      {Embedded Software Developer Intern}{Jan. 2019 -- Apr. 2019}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Sigmoid Academy} $|$ \emph{\href{https://sigmoid-academy.netlify.app/}{sigmoid-academy.netlify.app}}}{\emph{Jan. 2022 -- Present}}
          \resumeItemListStart
            \resumeItem{Orchestrated Django backend with JWT authentication, GitHub OAuth, and remote code execution}
            \resumeItem{Authored 20+ data science and machine learning coding challenges, including comprehensive tutorials}
            \resumeItem{Managed authentication and maintenance of user base of 200+ using PostgreSQL and Redis databases}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{STUMPY} $|$ \emph{\href{https://github.com/TDAmeritrade/stumpy}{github.com/TDAmeritrade/stumpy}}}{\emph{May 2021 -- Aug. 2023}}
          \resumeItemListStart
            \resumeItem{Published comprehensive tutorials on Matrix Profile annotation vectors based on research paper}
            \resumeItem{Implemented tiling scheme algorithm that leverages cache lines to improve computation speeds by up to 50\%}
            \resumeItem{Devised heuristic algorithm that can provide fast approximation to Matrix Profile}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-------------------------------------------

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {B.A.Sc. in Electrical Engineering}{Sep. 2018 -- Apr. 2023}
      \resumeItemListStart
        \resumeItem{Graduation with Distinction (GPA: 85.9/100)}
        \resumeItem{Specialization in Artificial Intelligence}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


\end{document}
